---
title: "Tidy Tuesday Work"
description: |
  All of my graphs from weekly Tidy Tuesday work
author:
  - name: Anthony Palma
date: 10-05-2021
preview: tt_image.jpeg
output:
  distill::distill_article:
    self_contained: false
---

Below are my assignments for the weekly Tidy Tuesday challenge.  

## Week 1:  Formula 1 Racing

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(tidytuesdayR)
library(rvest)
```

```{r, cache=TRUE}
tuesdata1 <- tidytuesdayR::tt_load('2021-09-07')
results <- tuesdata1$results
```

```{r, cache=TRUE}
driver_results_df <- tuesdata1$driver_standings %>% 
  left_join(tuesdata1$races, by = "raceId") %>% 
  rename(driver_url = url) %>% 
  left_join(tuesdata1$drivers, by = "driverId")
```


```{r, cache=TRUE}
driver_results_by_nationality <- driver_results_df %>%
                                    group_by(nationality) 
```

```{r, cache=TRUE}
df_Americans <- driver_results_by_nationality %>%
            filter(nationality == "American") %>%
            group_by(year) %>%
            summarize(total_wins = sum(wins))

```

```{r, cache=TRUE}
Americans <- df_Americans %>%
    ggplot(aes(x = year, y = total_wins)) +
    geom_line(color = "blue", size = 1) +
    labs(x = "Year", y = "Total Wins", title = "USA Formula 1 Race Wins Over The Years -- by Anthony Palma") 

```

```{r, cache=TRUE}
Americans + theme(
  panel.background = element_rect(fill = "orange", color = "#6D9EC1", size = 2, linetype = "solid"), 
  panel.grid.minor =  element_blank(), 
  panel.grid.major =  element_blank())




```

**Question:  How does number of wins trend over the years for American drivers?**

I am not a big F1 racing fan and was completely unaware of many American drivers being involved. I assumed, as there are many other nationality drivers, that it was more of a European centered sport. I chose to look at American wins over the years as I was curious to see how well American drivers have performed in a sport that I think is not super well known in America. As I suspected, I would guess it is not as well knwon possibly because of the trend seen above. With little American success (actually 0 wins since a bit before 1980), if someone wasn’t an avid fan they most likely would not know much as opposed to more American-centric sports like football.

## Week 2: Billboard Top Hits


```{r, cache=TRUE}
tuesdata2 <- tidytuesdayR::tt_load('2021-09-14')
billboard <- tuesdata2$billboard

```

```{r, cache=TRUE}
billboard_mod <- billboard %>%
                  select(week_position, instance, previous_week_position, peak_position, weeks_on_chart)
```


```{r, cache=TRUE}
billboard_graph_new <- billboard_mod %>%
    ggplot(aes(y = weeks_on_chart, x = peak_position)) +
    geom_line(color = "#151c73") +
    labs(x = "Weeks on the Chart", y = "Peak Billboard Position", title = "The Effect of Repeated Hit Songs on Speed to the Top of the Billboard List", subtitle = "Facet Wrapped by Instance -- by Anthony Palma") +
    facet_wrap(~instance, scales = "free_y", nrow = 2) 
```

```{r, cache=TRUE}
billboard_graph_new +
  theme(panel.background = element_rect(fill = "#ed8c0e"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        plot.background = element_rect(fill = "#151c73"), 
        text = element_text(color = "#FFFFFF"), 
        axis.text = element_text(color = "#FFFFFF"))

```


**Question:  How does speed to the top of the billboard list become altered by a song having been on the list before?**

I have heard of many songs going on and off the billboard top hits list.  I was curious as to how the speed to the top of the list is different for songs that only were popular for one stint compared to songs that went on and off the list many times, specifically on and off a lot of times.  As you can see, songs that are big hits one time only (ie on and off the list, not on and off several times) saw a very quick and steep rise to the top of the list (denoted by a steep slope down w massive y axis scale).  As the instance of the song increases, you can see less of a skew on the graph as opposed to the instance == 1 sharp right skew, denoting less of a rise beyond its initial instance.  Notice the free y axis scales and how even steeper rises to the top of the list (bottom of y axis) for increased instances does not compare in any way to the massive and exponential rise to the top of the list for instance == 1.  In summary, songs that are one hit wonders on the list skyrocket to the top with increased weeks on the chart resulting in higher peak position.  Songs that have been on the list already tend to start a bit higher on the list in its initial peak position yet as weeks go on, the rise to the top is wayyyyyy less drastic / evident (or even existent).     

## Week 3: Emmy Awards

```{r, cache=TRUE}
tuesdata3 <- tidytuesdayR::tt_load('2021-09-21')
nominees <- tuesdata3$nominees
```

```{r, cache=TRUE}
nominees_new <- 
  nominees %>%
  select(-logo, -page_id, -page)
```

```{r, cache=TRUE}
nominees_netflix <- nominees_new %>%
  filter(distributor == "Netflix")
```

```{r, cache=TRUE}
Netflix_graph_new <- nominees_netflix %>%
    ggplot(aes(x = year)) +
    geom_bar(stat = "count", fill = "#Aa1d1d") +
    facet_wrap(~type) +
  labs(y = "Count", x = "Year", title = "Netflix's Emmy Award Nominations Compared with Wins Over the Years", subtitle = "by Anthony Palma") 
```

```{r, cache=TRUE}
Netflix_graph_new +
   theme(panel.background = element_rect(fill = "#000000"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        plot.background = element_rect(fill = "#Aa1d1d"), 
        text = element_text(color = "#FFFFFF"), 
        axis.text = element_text(color = "#FFFFFF"))
```

**Question:  What does Netflix's Emmy Award performance look like over the years?**

Netflix is my favorite streaming platform which has had dozens of major hits over the last couple years.  I was curious as to how their rise in binge-worthy shows over the pandemic would be reflected in a faceted graph looking at nomination and winner of category counts for their shows. To no surprise, their content quality increased as I perceived, which can be seen with the rapid rise in Emmy nominated shows, peaking during the 2020 pandemic year (Note: 2021 was still very strong though). Surprisingly, their winner of category graph doesn't actually peak where their nominations graph does....the winner graph peaks just a bit after in 2021.  This could be because some of the back end quality 2020 films/shows were after the 2020 awards or it also could be because Netflix limited production to just their top hits in 2021 maximizing performance of shows and minimizing loss in a tough economic situation...


## Week 4: Nurse Salaries

```{r, cache=TRUE}
tuesdata <- tidytuesdayR::tt_load('2021-10-05')

```

```{r, cache=TRUE}
nurses <- tuesdata$nurses

```



```{r, cache=TRUE}
nurses_new <- nurses %>%
            filter(Year == "2020", 
                   State != "Virgin Islands") %>%
            select(State, Year, `Annual Salary Avg`, `Annual Salary Median`, `Total Employed RN`) %>%
            group_by(State) %>%
            mutate(inc_ineq_percent = (`Annual Salary Avg` - `Annual Salary Median`)/(`Annual Salary Median`)*100) %>%
            ungroup() 

```



```{r, cache=TRUE, out.width="600%"}
nurses_new %>%
    ggplot(aes(x = `Total Employed RN`, y = inc_ineq_percent)) +
    geom_point(size = 0.6, color = "red") +
    geom_text(aes(label= State), color = "navy", hjust=0, vjust=0, size=2, check_overlap = TRUE) +
    labs(x = "Total Number of RNs", 
         y = "Income Inequality Percent", 
        title = "Which States' Have a Greater Discrepancy In Pay for RN's?") +
    theme_classic() +
    theme(
    panel.background = element_rect(fill = "#CBC3E3"), 
    plot.background = element_rect(fill = "#CBC3E3"), 
    text = element_text(color = "navy")) 


    
```


**For a Pandemic Year, 2020, how does the proportion of income inequality, comparing average salary to median salary, compare across the country?** 

Income Inequality Calculation, represented as a % --> Inc Ineq = (Ann Salary Avg - Ann Salary Median) / Ann Salary Median

NOTE: Higher and positive Inc Ineq percent reveals a state with a significantly higher average salary than median salary, showing a higher discrepancy in pay with more nurses paid significantly more than the bulk.  A negative percent reveals a discrepancy where more nurses are significantly underpaid relative to the median salary than overpaid.  


I wanted to look at how different states pay to nurses compares to their median pay.  As you can see, most have "+" income inequality values meaning they have higher avg annual salaries than median annual salaries by a certain percent.  Because of the nature of how average is calculated compared to median, having a higher avg salary is a result of having much higher top salaries.  For the few with negative scores like Hawaii, this reflects a pool of nurses that are more significantly underpaid relative to the median than significantly overpaid like the bulk of the states.  While it may be a bit difficult to understand at first glance (of this calculation for a proxy of income inequality), having your average annual salary up to 5% higher than your average median salary is very interesting to see as it shows a big discrepancy in pay comparing the middle points with the outliers....One point to note is that as the number of nurses increase, the perceived income inequality goes down closer to 0...


## Week 5: CBS Survivor

```{r, cache=TRUE}
tuesdata <- tidytuesdayR::tt_load(2021, week = 23)

summary <- tuesdata$summary
```

```{r, cache=TRUE}
survivor <- 
  summary %>%
  select(season_name, season, country, viewers_premier) %>%
  mutate(premier_avg = mean(viewers_premier),
        premier_viewers_diff = viewers_premier - premier_avg)
  
```


```{r, cache=TRUE}
    ggplot(survivor, aes(x = season, y = viewers_premier)) +
    geom_line(size = 2, color = "#17c6e0") +
    geom_hline(yintercept = mean(survivor$viewers_premier), color = "red") +
    geom_hline(yintercept = median(survivor$viewers_premier), color = "blue") +
    labs(x = "Season Number", 
         y = "Premier Episode Viewership (millions)", 
        title = "Survivior Premier Viewership, with Reference to Average and Median Premier") +
    theme_classic() +
    theme(
    panel.background = element_rect(fill = "#Dae017"), 
    plot.background = element_rect(fill = "#17c6e0"), 
    text = element_text(color = "navy")) 
```

**How has Survivor enthusiasm changed over the seasons, as it relates to season premier viewership?** 


I am a Survivor Super Fan and have been watching with my family every season since I can remember.  I wanted to see how the enthusiasm for the show, as expressed in millions of viewers from the premier, has changed over time (with seasons =reflecting change over time).  To my surprise, the earlier seasons in which the game was much more simple saw a much higher level of enthusiasm compared with the newer more modern and advanced seasons.  Seeing a steady decline in premier viewership is incredibly surprising as I have found the more strategic and modern more recent seasons have been of more interest to me than the older more basic seasons....maybe it is a generational gap difference that can be seen in the changing viewership.  It is quite clear overall though that the mean premier viewership around 17-18 million is carried heavily by the large spikes around season 2 and 8 which explains the massive 4 million viewer discrepancy between average premier viewership and median premier viewership.   


